---
title: "HW5"
author: "ShibeiXu"
date: "2021/11/20"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r install libaray and set up environment,echo=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,fig.width = 6,fig.asp = .6,out.width = "90%")
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(ggplot2.continuous.colour = "viridis",ggplot2.continuous.fill = "viridis")
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
## Problem 1
Load the data, create a variable to check for the city and state and only select resolved status and the city variable
```{r,warning=FALSE,message=FALSE}
homicide_df = 
  read_csv("homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```
Summarize the total number of homicide cases and the number of unsolved homicide cases
```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```
Proportion of unsolved case in Baltimore
```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```
Proportion of unsolved case in all cities
```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```
Plot and check for error bar
```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```
## Problem 2
 Use list.file function to check the data
```{r,message=FALSE,warning=FALSE}
list.files("data")
data_1 = read_csv("data/con_01.csv")
```
In the data tidy and wrangling, first we use map function to read in the files, then we separate the control and experiment group and rename the variable. We pivot the variable weeks into longer format so the data is more understandable.
```{r}
export_df = 
  tibble(file_name = list.files("data", pattern = "*"))%>%
  mutate(data = map(.x = str_c("data/", file_name, sep=""), ~ read.csv(.x)))%>%
  separate(file_name, into = c("filename", "post"), sep = "\\.")%>%
  select(-post)%>%
  separate(filename, into = c("group", "id"), sep = "_", remove = F)%>%
  unnest(.)%>%
  pivot_longer(week_1:week_8,names_to = "week",values_to = "value")%>%
  separate(week, into = c("pre", "weeks"), sep = "_") %>% 
  select(-pre)
```
We create a spaghetti plot using variable weeks and value and group by control and experiment
```{r}
export_df %>% 
  ggplot(aes(x = weeks, y = value, group = filename, col = group)) +
  geom_line()
```
## Problem 3
First we load the data check for the missing value in this dataset
```{r}
library(tidyverse)
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))%>%
  janitor::clean_names()
```
Create a function to filling the missing data,we use the if function and define the replace value when a NA exist
```{r}
fill = function(d) {
  if (is.numeric(d)) {
    value_filled = round(mean(d, na.rm = TRUE),2)
    d = d %>% replace_na(value_filled)
  } 
  else if (is.character(d)) {
    d = d %>%replace_na('virginica')
  }
  d
}
```
Use map statement to apply for the missing value
```{r}
iris_full=iris_with_missing%>%
mutate(map_df(iris_with_missing,fill))
```
Check the data
We use the head function to check if missing value still exist
```{r}
head(iris_full,20)
```


